GVN-Hoist: Hoisting Computations from Branches

### 2016-08-14 hoist.tex
ranking

\subsection{Making the transformation}
Once all the legality checks and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed. After that SSA semantics is restored by updating the
intermediate representation (IR) to reflect changes.

@@

>>>>

\subsection{Making the transformation}
Once all the legality checks and profitability checks are satisfied for a set of
identical instructions, they are suitable candidates for hoisting. A copy of the
computation is inserted at the hoisting point along with any instructions which
needed to be rematerialized. Thereafter, all the computations made redundant by
the new copy are removed. After that SSA form is restored by updating the
intermediate representation (IR) to reflect changes. After one iteration of
algorithm runs through the entire function, it creates more oppportunities for
\italics{higher ranked} computations \cite{rosen1988global}. Currently, we rerun
the algorithm until there are no more instructions left to be
hoisted. Obviously, this is not the most optimal approach and can be improved by
ranking the computations \cite{rosen1988global}.

@@

Currently, we rerun the algorithm until there are no more instructions left to
be hoisted. This is not the most optimal approach and results in expensive
analyses to be recomputed. This can be improved by ranking the computations
\cite{rosen1988global}.
